### 2016-10-15 resume/education.tex
working on elliptic
starting new semester
updated resume

\noindent\textbf{\large Education}
\begin{enumerate}[label={\Roman*}.]
\item \textbf{Christopher Newport University $\cdot$ 2013 - Present}\\
Bachelors of Science $-$ Mathematics $\cdot$ Bachelors of Science $-$ Computer Science
\begin{itemize}
\item Community Involvement and Accomplishments
\begin{itemize}
\item Employed by the Center for Academic Success as a tutor in Mathematics and Computer Science
\item Inducted into the Virginia Mu chapter of Pi Mu Epsilon
\item Served as Secretary for the Society of Physics club
\item Earned Dean's List consistently
\end{itemize}
% \newpage
\item Relevant coursework includes
\begin{itemize}
\item Mathematical Education
\begin{quote}
Calculus I - IV, Linear Algebra, Real Analysis, Partial and Ordinary Differential Equations, Writing in
Mathematics using \hologo{LaTeX}, Proofs and Discreet Mathematics, Number Theory, Independent Study in
Partial Differential Equations
\end{quote}
\item Computer Science Education
\begin{quote}
UNIX Operating Systems, C++ Programming, Java Programming, Android Programming, Programming Language
Concepts, Data Structures, Algorithms, Computer Hardware and Design, Discreet Mathematics
\end{quote}
\end{itemize}
\end{itemize}
\end{enumerate}

>>>>

\noindent\textbf{\large Education}
\begin{enumerate}[label={\Roman*}.]
	\item \textbf{Christopher Newport University $\Bigcdot$ August 2013 - May 2017}\\
	      Bachelors of Science $-$ Mathematics $\cdot$ Bachelors of Science $-$ Computer Science $\cdot$ 3.67 GPA
	      \begin{itemize}
	      	\item Community Involvement and Accomplishments
	      	      \begin{itemize}
	      	      	\item Employed by the Center for Academic Success as a tutor in Mathematics and Computer Science
	      	      	\item Inducted into the Virginia Mu chapter of Pi Mu Epsilon
	      	      	\item Served as Secretary for the Society of Physics club
	      	      	\item Served as Secretary for Math club
	      	      	\item Earned Dean's List since Fall 2013
	      	      \end{itemize}
	      	\item Relevant coursework includes
	      	      \begin{itemize}
	      	      	\item Mathematics Education
	      	      	      \begin{quote}
	      	      	      	\def\arraystretch{1.1}
	      	      	      	\begin{tabular}{l l l}
	      	      	      		Calculus I - IV                            & Linear Algebra         & Real Analysis                         \\
	      	      	      		Group Theory                               & Differential Equations & Technical Writing with \hologo{LaTeX} \\
	      	      	      		Proofs and Discreet Mathematics            & Number Theory          & \textit{p-adic} Analysis              \\
	      	      	      		Research in Partial Differential Equations & Mathematical Modeling  & Programming in Mathematica
	      	      	      	\end{tabular}
	      	      	      \end{quote}
	      	      	\item Computer Science Education
	      	      	      \begin{quote}
	      	      	      	\def\arraystretch{1.1}
	      	      	      	\begin{tabular}{l l l}
	      	      	      		UNIX Operating Systems & C++ Programming & Java Programming              \\
	      	      	      		Android Programming    & Software Design & Programming Language Concepts \\
	      	      	      		Data Structures        & Algorithms      & Computer Hardware and Design  \\
	      	      	      		Discreet Mathematics & Writing and Computer Ethics
	      	      	      	\end{tabular}
	      	      	      \end{quote}
	      	      	\item Programming Language and Framework Experience
	      	      	      \begin{quote}
	      	      	      	\def\arraystretch{1.1}
	      	      	      	\begin{tabular}{c  c  c}
	      	      	      		\textbf{Proficient} & \textbf{Advanced}     & \textbf{Intermediate} \\
	      	      	      		\hline
	      	      	      		Java/Android        & PHP                   & C\#/Unity             \\
	      	      	      		\LaTeX              & Javascript/Angular.js & Swift/iOS             \\
	      	      	      		Ruby                & C/C++                 & Objective-C           \\
	      	      	      		Lua                 & Python                &                       \\
	      	      	      		                    & Mathematica           &
	      	      	      	\end{tabular}
	      	      	      \end{quote}
	      	      \end{itemize}
	      \end{itemize}
\end{enumerate}

### 2016-10-15 resume/work.tex
updated resume

\item MyNewLeaf, LLC $\Bigcdot$ January 2016 - Present
\begin{itemize}
\item Contracted to develop Android version of iOS application
\item Collaborated with a large team of designers, managers, and programmers
\item Served as lead programmer for Android version of application
\end{itemize}

\item National Aeronautics and Space Administration (NASA) $\Bigcdot$ November 2015 - Present
\begin{itemize}
\item Developed Android applications for Google Glass, Vuzix M100, and Recon Jet headsets
\item Worked closely with a university professor to plan and create the application
\item Participated in laser safety training and received laser operator certification

@@

\item Application Developer $\Bigcdot$ July 2015 - Present
\begin{itemize}
\item Built a location based audio application called Audionce, written for Android and iOS
\item Created a quiz web-application called WhensIt for the Public History Center at Christopher Newport
University
\item Built websites using JavaScript, HTML5, CSS3, and PHP
\end{itemize}

\item Christopher Newport University $\Bigcdot$ September 2013 - Present
\begin{itemize}
\item Tutor for the Center for Academic Success (Fall 2015 - Present)
\begin{itemize}
\item Tutored several subjects including Mathematics (mostly Calculus), Computer Engineering, and
Computer Science
\item Participated in both one on one tutoring and group tutoring
\item Created various resources for other Calculus tutors to use
\end{itemize}
\item IT Customer Service Representative (Fall 2014 - Spring 2016)
\begin{itemize}
\item Aided customers with various software related IT issues
\item Assisted technicians with tasks such as installing hardware
\end{itemize}
\end{itemize}

\newpage
\item Kirk Family YMCA $\Bigcdot$ August 2009 - August 2015
\begin{itemize}
\item Lead Swim Instructor
\begin{itemize}
\item Managed a team of swim instructors that taught and oversaw various camps and lessons
\item Taught swimming lessons to children and adults of all ages
\item Promoted to manager in May 2015
\end{itemize}
\item Lifeguard
\begin{itemize}
\item Attended trainings for CPR and AED certifications, as well as First Aid and lifesaving skills
\item Worked to create and maintain a safe environment for all patrons of the pool by enforcing rules and
policies of the YMCA
\end{itemize}
\end{itemize}
\end{enumerate}

>>>>

\item \textbf{MyNewLeaf, LLC $\Bigcdot$ January 2016 - Present}
\begin{itemize}
\item Contracted to develop Android version of iOS application
\item Collaborated with a large team of designers, managers, and programmers
\item Served as lead programmer for Android version of application
\item Contributed to UI design process
\end{itemize}

\item \textbf{National Aeronautics and Space Administration (NASA) $\Bigcdot$ November 2015 - Present}
\begin{itemize}
\item Developed Android applications for Google Glass, Vuzix M100, and Recon Jet headsets
\item Worked closely with a university professor to plan, create, and design the application
\item Created universal application for a wide range of Android powered devices
\item Participated in laser safety training and received laser operator certification

@@

% \item \textbf{Application Developer $\Bigcdot$ July 2015 - Present}
% \begin{itemize}
% \item Built a location based audio application called Audionce, written for Android and iOS
% \item Created a quiz web-application called WhensIt for the Public History Center at Christopher Newport
% University
% \item Built websites using JavaScript, HTML5, CSS3, and PHP
% \end{itemize}

\item \textbf{Christopher Newport University $\Bigcdot$ September 2014 - Present}
\begin{itemize}
\item Tutor for the Center for Academic Success (Fall 2015 - Present)
\begin{itemize}
\item Tutored several subjects including Mathematics, Computer Engineering, and Computer Science
\item Participated in both one on one tutoring and group tutoring
\item Created various resources for other tutors
\item Participated in group training exercises to receive tutor certification 
\end{itemize}
\item IT Customer Service Representative (Fall 2014 - Spring 2016)
\begin{itemize}
\item Aided customers with various software related IT issues
\item Assisted technicians with tasks such as installing hardware
\end{itemize}
\end{itemize}

\newpage
\item \textbf{Kirk Family YMCA $\Bigcdot$ August 2009 - August 2015}
\begin{itemize}
\item Lead Swim Instructor
\begin{itemize}
\item Managed a team of swim instructors that taught and oversaw various camps and lessons
\item Taught swimming lessons to children and adults of all ages
\item Promoted to manager in May 2015
\end{itemize}
\item Lifeguard
\begin{itemize}
\item Attended trainings for CPR and AED certifications, as well as First Aid and lifesaving skills
\item Worked to create and maintain a safe environment for all patrons of the pool by enforcing rules and
policies of the YMCA
\end{itemize}
\end{itemize}
\end{enumerate}
